Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-17 outputs/paper/paper.qmd
Paper Edits

```{r}
#install.packages('haven')
#install.packages('here')

@@

#raw_data <- read_dta(here::here("inputs/data/survey.dta"))

#dat_male <- dat_use[dat_use$gender == "Male"

#raw_data$gender

#raw_data <- raw_data[raw_data$gender == "Male"]
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

@@

# References

>>>>

```{r}
#| echo: false
#install.packages('haven')
#install.packages('here')

@@

#survey_data <- read_dta(here::here("inputs/data/survey_cleaned.csv"))
```

@@

# References {.unnumbered}
